\tool: Revisiting BadUSB with Type-C

### 2021-01-28 WOOT/Files/conclusion.tex
complete conclusion part

\section{Conclusion}
\label{sec:conclusion}
\outline{Conclusion}

>>>>

\section{Conclusion}
\label{sec:conclusion}
\outline{Conclusion}
Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a new attack scheme named \tool and three useful attack modes. Each of these three modes has its own strength and use case. The scripting mode largely extends the original BadUSB and successfully bypasses existing defenses. The privacy extraction mode proved practical and powerful in the user study, as it extracts victim's privacy in a stealth way. The remote control mode archives complete hijack of target device, allowing us to perform various type of subsequent attacks. By experimenting \tool in three different devices, we further tests its ability under different mode and proves it can indeed bypass certain defense like GoodUSB~\cite{tian2015defending}. In user study, we obtains and analyzes video stream extracted from 10 participant with \tool, which demonstrates its capability in real life scenario. In the end, we propose a new defense scheme named \textit{isolated UI rendering}, which can effectively stop our \tool.

As future work, we decide to further explore the potential of \textit{isolated UI rendering} and implement it on a customized operating system. Moreover we also hope to lower the power and network requirement of \tool to make it more practical.

### 2021-01-28 WOOT/Files/countermeasure.tex
complete conclusion part

\textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
its {trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
is worth mentioning that \textit{distrust-by-default} policy is not the same as
GoodUSB~\cite{tian2015defending}.  \fengwei{the following sentence needs to be
written. I am confused.} GoodUSB relies on the {unauthorized} device to
complete its own authorization, while in this strict policy, users have to use
an {authorized} device. Though \textit{distrust-by-default} policy effectively
prevents these attacks, it also causes considerable inconvenience for users.
For example, when there is no other {authorized} device plugged, it is
impossible for users to complete the authorization in the first place. Thus
this strict policy is far from optimal in most use cases.

\textbf{Isolated UI Rendering.} During our experiments, we noticed that \tool
is actually unable to redirect out the locking screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the locking screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated UI Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one
is secure the other is insecure. When an application require to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only pass it to the secure driver, which only shows the sensitive content
(e.g., a keyboard) on the internal display. For the rest of the rendering, it
would render on both internal and external display (e.g., insensitive
contents). \fengwei{we need more text to describe the figure}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}%\shuqing{Maybe we can increase the font?}
	\label{fig:isolated_ui}
\end{figure}
\fengwei{what are untrusted and trusted screens? are they internal and external displays?}

>>>>

\textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
is worth mentioning that \textit{distrust-by-default} policy is not the same as
GoodUSB~\cite{tian2015defending}.  \fengwei{the following sentence needs to be
written. I am confused.}\hongyi{Fixed, use more concise sentences} GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
prevents these attacks, it also causes considerable inconvenience for users.

\textbf{Isolated UI Rendering.} During our experiments, we noticed that \tool
is actually unable to redirect out the locking screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the locking screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated UI Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated UI render layer and corresponding driver, one
is secure the other is insecure. When an application require to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive. Thus, the `password' and `keyboard' are not rendered on untrusted screen as they contains private information.
 \fengwei{we need more text to describe the figure}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}%\shuqing{Maybe we can increase the font?}
	\label{fig:isolated_ui}
\end{figure}
\fengwei{what are untrusted and trusted screens? are they internal and external displays?}
\hongyi{Fixed by using the same term and additional description}

### 2021-01-28 WOOT/Files/experiment.tex
fix some suggestions in imple
complete conclusion part

\textit{Setup.} \fengwei{I would suggest to add references for devices such as
Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
computer inside \tool, which is powerful enough to process video data and has
onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board~\cite{atmel}
with USB protocol support. This Atmel chip is able to emulate most HID devices
with our modified firmware. About the USB 3.x hub, we uses one from the
UGREEN, which supports HDMI, USB 2.0, and many other exported peripheral.
Apart from these essential parts, we also uses an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
2, 3, 4, and 5?}

\begin{figure}[t]
	\centering
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}
	\caption{\tool}
	\label{fig:armory}
\end{figure}

@@

@@

\fengwei{I don't understand the following sentence. Both modes need to capture
the video stream. Don't understand why it is more power-efficient.} After the
experiment, we have found that as privacy extraction mode only passively
process victim's video stream, this is a more power-efficient mode than remote
control mode.

>>>>

\textit{Setup.} \fengwei{I would suggest to add references for devices such as
Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
computer inside \tool, which is powerful enough to process video data and has
onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board~\cite{atmel}
with USB protocol support. This Atmel chip is able to emulate most HID devices
with our modified firmware. About the USB 3.x hub, we uses one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripheral.
Apart from these essential parts, we also uses an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}

\begin{figure}[t]
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
	\mycircled{5}ATMEGAA32U4 Board
	\end{tabular}

	\caption{\tool}
	\label{fig:armory}
\end{figure}

@@

\fengwei{I don't understand the following sentence. Both modes need to capture
the video stream. Don't understand why it is more power-efficient.}
\hongyi{Reasonable, changed to other advantage} 
After the
experiment, we have found that as privacy extraction mode only needs to
process victim's video stream locally, it does not need to transmit the real-time video back to the attacker. This mode is useful when there is no stable network connection between \tool and attacker.

@@
